---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# devubesp

<!-- badges: start -->
<!-- badges: end -->

The goal of devubesp is to automate analyses setup tasks that are
otherwise performed manually. This includes setting up directories,
supporting packages and projects.

## Installation

You can install the development version from
[GitHub](https://github.com/) with the following procedure:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("CorradoLanera/devubesp")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example, eval=FALSE}
library(devubesp)
## basic example code
```


## Code of Conduct
Please note that the 'devubesp' project is released with a
[Contributor Code of Conduct](.github/CODE_OF_CONDUCT.md).
By contributing to this project, you agree to abide by its terms.
