---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# devubesp

<!-- badges: start -->
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/CorradoLanera/devubesp?branch=master&svg=true)](https://ci.appveyor.com/project/CorradoLanera/devubesp)
[![Travis build status](https://travis-ci.org/CorradoLanera/devubesp.svg?branch=master)](https://travis-ci.org/CorradoLanera/devubesp)
[![Codecov test coverage](https://codecov.io/gh/CorradoLanera/devubesp/branch/master/graph/badge.svg)](https://codecov.io/gh/CorradoLanera/devubesp?branch=master)
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![CRAN status](https://www.r-pkg.org/badges/version/devubesp)](https://cran.r-project.org/package=devubesp)
<!-- badges: end -->

The goal of devubesp is to automate analyses setup tasks that are
otherwise performed manually. This includes setting up directories,
supporting packages and projects.

## Installation

You can install the development version from
[GitHub](https://github.com/) with the following procedure:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("CorradoLanera/devubesp")
```

## Example

The package, _de facto_, provide a single function. The aim of the 
function ``create_ubesp_analysis()` is to setup all the folders'
structure, with all the needed and sample files to conduct analyses
at UBESP. Does not matter if they are for a thesis, a project, a simple analyses, the initial structure for the project should be the same.

The main characteristics are:

  - presence of folder (`analyses/`) that can be safely copy-pasted to a
    costumer folder or to an external one (e.g., SharePoint). It will 
    contains all the reports, outputs, and script useful to easily 
    find the results and also to reproduce them.
    
  - presence of an external folder to collect and manage *data-raw*
    which can be huge, sensitive, and so often they cannot be shared or
    uploaded on the net (e.g., on GitHub). On the other hand, the folder
    itself can be copy-pasted to a costumer folder or to an external
    one (e.g., SharePoint), if usefull and admitted.
    
  - presence of a package-folder infrastructure which can be use to 
    safely implement/include any custom or additional function usefull
    for the analyses. This can be VCS with git and GitHub safely, 
    without risk to fill the space with data. Moreover, the folder
    `analyses` is inside the package main folder but it is
    `.Rbuildignored`, this means that can be git-tracked but it is not
    provided in the package boundle. Hence, the package can be safely
    shared both through GitHub or CRAN without risk to share data or 
    anayses.
    
  - presence of folders and files to track:
  
    - literature used
    - papers written (in all the draft, submitted and published shape)
    - minutes
    - proposal
    - personal and private notes or comments not to be shared. 
  

This is a basic example which shows you how to simple it is to be
used:^[the tilda ("`~`"), here, expands to the home directory from the
"r point-of-view", i.e. the classical home/ on Unix systems, but to the
"user/documents" on windows (instead of the simple "user/").]


```{r example, eval=FALSE}
devubesp::create_ubesp_analysis("~/test")
```

## Feature request
If you need some more features, please file an issue on
[github](https://github.com/CorradoLanera/devubesp/issues).


## Bug reports
If you encounter a bug, please file a
[reprex](https://github.com/tidyverse/reprex)
(minimal reproducible example) on
[github](https://github.com/CorradoLanera/devubesp/issues).


## Code of Conduct
Please note that the "devubesp" project is released with a
[Contributor Code of Conduct](.github/CODE_OF_CONDUCT.md).
By contributing to this project, you agree to abide by its terms.
